opXRD: Open Experimental Powder X-ray Diffraction Database

### 2025-04-29 chapters/03_existing_datasets.tex
Update

\begin{table}[!htb]
\centering
\caption{\footnotesize Overview of experimental powder diffraction databases: The column ``O.A.'' indicates whether or not the database is open-access. The availability of the chemical composition, spacegroups, lattice parameters, and \replaced{basis}{atomic coordinates} of the underlying samples are indicated by the columns ``Comp.'', ``Spg.'', ``Lattice'' and ``Atom coords.'', respectively.}
\label{tab:exp_databases}
\scalebox{0.85}{
\begin{adjustbox}{center}
\begin{NiceTabular}{@{}llllllll@{}}[columns-width=1.2cm]
\toprule
\textbf{Name} & \textbf{No. patterns} & \textbf{O.A.} & \textbf{Comp.} & \textbf{Spg.} & \textbf{Lattice} & \textbf{Basis} & \textbf{Year est.} \\
\midrule
Linus Pauling file                     & 21,700                    & \xmark          & \cmark        & \cmark        & \cmark        & \cmark          & 2002            \\
Powder Diffraction File \tabularnote[a)]{The PDF lists the Material Platform for Data Science (MPDS) as a database source. Since the MPDS is hosted by the Pauling File project, there is likely significant overlap in the experimental patterns available in the PDF and the Linus Pauling File.} & 20,800 & \xmark & \cmark & \cmark & \cmark & \pchk{52} & 1941 \\
RRUFF                                  & 1290                      & \cmark          & \cmark        & \cmark        & \cmark        & \xmark          & 2006            \\
Crystallography Open Database          & 1052                      & \cmark          & \cmark        & \cmark        & \pchk{85}     & \pchk{85}       & 2003            \\
PowBase                                & 169                       & \cmark          & \cmark        & \xmark        & \xmark        & \xmark          & 1999            \\
\bottomrule
\end{NiceTabular}
\end{adjustbox}}
\end{table}

>>>>

\begin{table}[!htb]
\centering
\caption{\footnotesize Overview of experimental powder diffraction databases: The column ``O.A.'' indicates whether or not the database is open-access. The availability of the chemical composition, spacegroups, lattice parameters, and \replaced{the full structure}{atomic coordinates} of the underlying samples are indicated by the columns ``Comp.'', ``Spg.'', ``Lattice'' and ``Full structure'', respectively.}
\label{tab:exp_databases}
\scalebox{0.82}{
\begin{adjustbox}{center}
\begin{NiceTabular}{@{}llllllll@{}}[columns-width=1.2cm]
\toprule
\textbf{Name} & \textbf{No. Patterns} & \textbf{O.A.} & \textbf{Comp.} & \textbf{Spg.} & \textbf{Lattice} & \textbf{Full} & \textbf{Year est.} \\
& & & & & & \textbf{Structure} & \\
\midrule
Linus Pauling file                     & 21,700                    & \xmark          & \cmark        & \cmark        & \cmark        & \cmark          & 2002            \\
Powder Diffraction File \tabularnote[a)]{The PDF lists the Material Platform for Data Science (MPDS) as a database source. Since the MPDS is hosted by the Pauling File project, there is likely significant overlap in the experimental patterns available in the PDF and the Linus Pauling File.} & 20,800 & \xmark & \cmark & \cmark & \cmark & \pchk{52} & 1941 \\
RRUFF                                  & 1290                      & \cmark          & \cmark        & \cmark        & \cmark        & \xmark          & 2006            \\
Crystallography Open Database          & 1052                      & \cmark          & \cmark        & \cmark        & \pchk{85}     & \pchk{85}       & 2003            \\
PowBase                                & 169                       & \cmark          & \cmark        & \xmark        & \xmark        & \xmark          & 1999            \\
\bottomrule
\end{NiceTabular}
\end{adjustbox}}
\end{table}

### 2025-04-29 chapters/04_our_dataset.tex
Update

In collaboration with several other research institutions, we have collected a database of $\numpatterns$ experimental \added{powder diffraction} patterns. \added{Of these patterns, $\numlabeled$} are at least partially labeled with structural information \added{and $\numfull$ are fully labeled through the lattice and basis of the underlying material}. The following research institutions contributed data to the opXRD database: The French National Centre for Scientific Research (CNRS), Hong Kong University of Science and Technology (Guangzhou) (HKUST), University of Southern California (USC), Lawrence Berkeley National Laboratory (LBNL), Empa–Swiss Federal Laboratories for Materials Science and Technology (EMPA) and the Karlsruhe Institute of Technology (KIT). \added{We have taken measures to ensure data validation through both manual and automated processes. Before parsing the data we established the file formats and data organization of each submission to ensure that the files were compatible with our custom parsing mechanism. As part of the automatic parsing process,} we filtered the submitted datasets to exclude patterns with invalid features such as only one unique recorded angle, negative angles, less than 50 recorded angles total, or all intensities being zero. \added{After the parsing, we also manually inspected a random selection of patterns from each submitted dataset for any anomalies that would warrant further investigation.}

@@

\begin{table}[!htb]
\centering
\caption{\footnotesize Overview of the contributions to the opXRD database: The availability of the chemical composition, spacegroups, lattice parameters, and atomic coordinates of the underlying samples are indicated by the columns ``Comp.'', ``Spg.'', ``Lattice'' and ``\replaced{Basis}{ Atom coords}.'' respectively.}
\label{tab:merged}
\scalebox{0.81}{
\begin{adjustbox}{center}
\begin{NiceTabular}{@{}llllllll@{}}[columns-width=1.2cm]
\toprule
\textbf{\ Institution} & \textbf{No. patterns} & \textbf{Comp.} & \textbf{Spg.} & \textbf{Lattice} & \textbf{Basis} & \textbf{Research Project} \\
\midrule
\ CNRS        &  1052         &  \cmark   & \pchk{85}  & \cmark    &   \pchk{85}   & Diffraction data extracted from the COD \\ 
\ USC         &  338          &  \cmark   & \cmark     & \pchk{90} &   \xmark   & Study of CuNi and CuAl alloys          \\
\ HKUST(GZ)   &  520          &  \pchk{4} & \pchk{4}   & \pchk{4}  &   \pchk{4}   & Phase identification dataset  \\ 
\ EMPA        &  770          & \cmark    & \pchk{63}  & \xmark    &   \xmark   & Metal halide perovskites, Zn-V-N libraries \\ 
\ INT         &  19,796       & \xmark    & \xmark     & \xmark    &   \xmark   & Compilation of various projects        \\ 
\ IKFT        &  64           & \xmark    & \xmark     & \xmark    &   \xmark   & Commercial catalysts, metals, metal oxides   \\ 
\ LBNL        &  70,012       & \xmark    & \xmark     & \xmark    &   \xmark   & Perovskites precursors, Mn-Sb-O system  \\ 
\midrule
\midrule
\added{\ $\sum$ Labeled}   & \added{2,179}  & \pchk{79}  & \pchk{66}  & \pchk{63}  & \pchk{42} & \added{Partially and fully labeled opXRD data} \\
\added{\ $\sum$ Unlabeled }& \added{90,373} & \xmark     & \xmark     & \xmark     & \xmark    & \added{Unlabeled opXRD data}\\
\bottomrule
\end{NiceTabular}
\end{adjustbox}}
\end{table}

>>>>

In collaboration with several other research institutions, we have collected a database of $\numpatterns$ experimental \added{powder diffraction} patterns. \added{Of these patterns, $\numlabeled$} are at least partially labeled with structural information \added{and $\numfull$ are labeled with the full crystal structure of the underlying material}. The following research institutions contributed data to the opXRD database: The French National Centre for Scientific Research (CNRS), Hong Kong University of Science and Technology (Guangzhou) (HKUST), University of Southern California (USC), Lawrence Berkeley National Laboratory (LBNL), Empa–Swiss Federal Laboratories for Materials Science and Technology (EMPA) and the Karlsruhe Institute of Technology (KIT). \added{We have taken measures to ensure data validation through both manual and automated processes. Before parsing the data we established the file formats and data organization of each submission to ensure that the files were compatible with our custom parsing mechanism. As part of the automatic parsing process,} we filtered the submitted datasets to exclude patterns with invalid features such as only one unique recorded angle, negative angles, less than 50 recorded angles total, or all intensities being zero. \added{After the parsing, we also manually inspected a random selection of patterns from each submitted dataset for any anomalies that would warrant further investigation.}

@@

\begin{table}[!htb]
\centering
\caption{\footnotesize Overview of the contributions to the opXRD database: The availability of the chemical composition, spacegroups, lattice parameters, and \replaced{the full structure}{atomic coordinates} of the underlying samples are indicated by the columns ``Comp.'', ``Spg.'', ``Lattice'' and ``\replaced{Full structure}{ Atom coords}.'' respectively.}
\label{tab:merged}
\scalebox{0.81}{
\begin{adjustbox}{center}
\begin{NiceTabular}{@{}llllllll@{}}[columns-width=1.2cm]
\toprule
\textbf{\ Institution} & \textbf{No. Patterns} & \textbf{Comp.} & \textbf{Spg.} & \textbf{Lattice} & \textbf{Full} & \textbf{Research Project} \\
& & & & & \textbf{Structure} & \\
\midrule
\ CNRS        &  1052         &  \cmark   & \pchk{85}  & \cmark    &   \pchk{85}   & Diffraction data extracted from the COD \\ 
\ USC         &  338          &  \cmark   & \cmark     & \pchk{90} &   \xmark   & Study of CuNi and CuAl alloys          \\
\ HKUST(GZ)   &  520          &  \pchk{4} & \pchk{4}   & \pchk{4}  &   \pchk{4}   & Phase identification dataset  \\ 
\ EMPA        &  770          & \cmark    & \pchk{63}  & \xmark    &   \xmark   & Metal halide perovskites, Zn-V-N libraries \\ 
\ INT         &  19,796       & \xmark    & \xmark     & \xmark    &   \xmark   & Compilation of various projects        \\ 
\ IKFT        &  64           & \xmark    & \xmark     & \xmark    &   \xmark   & Commercial catalysts, metals, metal oxides   \\ 
\ LBNL        &  70,012       & \xmark    & \xmark     & \xmark    &   \xmark   & Perovskites precursors, Mn-Sb-O system  \\ 
\midrule
\midrule
\added{\ $\sum$ Labeled}   & \added{2,179}  & \pchk{79}  & \pchk{66}  & \pchk{63}  & \pchk{42} & \added{Partially and fully labeled opXRD data} \\
\added{\ $\sum$ Unlabeled }& \added{90,373} & \xmark     & \xmark     & \xmark     & \xmark    & \added{Unlabeled opXRD data}\\
\bottomrule
\end{NiceTabular}
\end{adjustbox}}
\end{table}

### 2025-04-29 main.tex
Added .json description
Improved table formatting
Finalized changes @ 14:41 29.04.25
Update

\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}[1][]{\textcolor{green!80!black}{#1\quad\ding{52}}}
\newcommand{\xmark}[1][]{\textcolor{red}{#1\quad\ding{53}}}
\newcommand{\partialcheck}[1]{\textcolor{orange}{\quad\ding{52}(#1\%)}}
\captionsetup[table]{font=footnotesize}

\date{}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\renewcommand\Authfont{\small\raggedright\itshape}  
\renewcommand\Affilfont{\normalfont\small}
\newcommand{\numpatterns}{92,552 }
\newcommand{\numlabeled}{2179 }

\DeclareSIUnit{\myeuro}{\text{\euro}}
\DeclareSIUnit\angstrom{\text {Å}}
\usepackage[final]{changes}

@@

\subsection*{Data availability}
The opXRD database is available on Zenodo at \url{https://zenodo.org/records/14254270}. It is published under the Creative Commons Attribution 4.0 International license. It can be downloaded by any user without any barriers or restrictions. For further details, please refer to Section~$\eqref{sec:how_to_use}$.

>>>>

\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}[1][]{\textcolor{green!80!black}{#1\ding{52}}}
\newcommand{\xmark}[1][]{\textcolor{red}{#1\ding{53}}}
\newcommand{\pchk}[1]{\textcolor{orange}{#1\%}}
\captionsetup[table]{font=footnotesize}

\date{}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\renewcommand\Authfont{\small\raggedright\itshape}  
\renewcommand\Affilfont{\normalfont\small}
\newcommand{\numpatterns}{92,552 }
\newcommand{\numlabeled}{2179 }
\newcommand{\numfull}{912 }

\DeclareSIUnit{\myeuro}{\text{\euro}}
\DeclareSIUnit\angstrom{\text {Å}}
\usepackage{changes}

@@

\subsection*{Data availability}
\replaced{The opXRD database is available on Zenodo at \url{https://zenodo.org/records/15298026}.}{The opXRD database is available on Zenodo at \url{https://zenodo.org/records/14254270}.}\added{The database version this manuscript refers to is v11 on Zenodo.} \replaced{opXRD}{It} is published under the Creative Commons Attribution 4.0 International license. It can be downloaded by any user without any barriers or restrictions. For further details, please refer to Section~$\eqref{sec:how_to_use}$.
